---
name: Kate
surname: Dibiasky
position: "PhD Candidate"
profilepic: "img/kate.jpeg"
address: "School of Astronomy, Michigan State University"
# phone: +1 22 3333 4444
# www: mariecurie.com
email: "k.dibiasky@gmail.com"
twitter: DontLookUpFilm
github: shaziaruybal/automate-cv-rmd
# linkedin: mariecurie
aboutme: "I have recently discovered Comet Dibiasky that is approximately 10-15km in size, and based on my orbital calculations is estimated to strike Earth in 6 months and 14 days"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(here)
```

```{r functions}
readExcelSheets <- function(filename){
  # read all sheets in .xlsx 
  all <- readxl::excel_sheets(filename)
  
  # import each sheet into a list using readxl::read_excel
  list <- lapply(all, function(x) readxl::read_excel(filename, sheet = x))
  
  # save sheet name for each sheet (list)
  names(list) <- all
  
  # breaks up list and creates a dataframe for each sheet with df names matching sheet names
  list2env(list, envir = .GlobalEnv)
}
```

```{r load-data, message=F, results='hide'}
filename <- here::here("kate_dibiasky_vitae_cv", "dibiasky_vitae_data.xlsx")

readExcelSheets(filename)
```

<!-- # Some stuff about me -->

<!--  * I poisoned myself doing research. -->
<!--  * I was the first woman to win a Nobel prize -->
<!--  * I was the first person and only woman to win a Nobel prize in two different sciences. -->

# Education
I am a Teaching Assistant in the Astronomy Department and am passionate about playing a positive role in shaping the new generation of astronomers. 


```{r}
# library(tibble)
# tribble(
#   ~ Degree, ~ Year, ~ Institution, ~ Where,
#   "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
#   "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
#   "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
# ) %>% 
#    detailed_entries(Degree, Year, Institution, Where)

education %>% 
  detailed_entries(what = degree,
                   when = year,
                   with = institution,
                   where = where,
                   why = details)
```

# Research experience
```{r}
research %>% 
  detailed_entries(what = role,
                   when = dates,
                   with = institution,
                   where = where,
                   why = details)
```


# Industry experience
```{r}
industry %>% 
  detailed_entries(what = role,
                   when = dates,
                   with = institution,
                   where = where,
                   why = details)
```

# Leadership experience
```{r}
leadership %>% 
  detailed_entries(what = role,
                   when = dates,
                   with = institution,
                   where = where,
                   why = details)
```

\newpage

# Language skills
```{r}
skills %>% 
  brief_entries(when = skill) # ,
                # with = level)
```

<!-- # Nobel Prizes -->

<!-- ```{r} -->
<!-- tribble( -->
<!--   ~Year, ~Type, ~Desc, -->
<!--   1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel", -->
<!--   1911, "Chemistry", "Awarded for the discovery of radium and polonium" -->
<!-- ) %>% -->
<!-- brief_entries( -->
<!--   glue::glue("Nobel Prize in {Type}"), -->
<!--   Year, -->
<!--   Desc -->
<!-- ) -->
<!-- ``` -->

# Publications

```{r}
# library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "packages.bib")
# 
# bibliography_entries("packages.bib") %>%
#   arrange(desc(author$family), issued)
# 
bibliography_entries(here("kate_dibiasky_vitae_cv", "papers.bib")) 
```

## Another way to display publications is using R Markdown. You can also use latex commands throughout the document:

\setlength{\leftskip}{0cm}
**2022**

\setlength{\leftskip}{1cm}
[**Dibiasky, K.** and Mindy, R. (2022). *Discovery of a novel comet, Comet Dibiasky, heading towards Earth.* Science.](https://media.giphy.com/media/q9CS6tp1oM45pmj19U/giphy.gif) 